### 2020-05-20 writeup/intro.tex
wip

Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).

@@

\begin{figure}[!t]
	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
	\caption{Phase transition as a parameter of model distance.}
	\label{fig_motivation}
\end{figure}

>>>>

%Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
%Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
In multi-task learning, having related task data is fundamental to its performance.
Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
For example, many applications in computer vision \cite{ZSSGM18}, natural language processing \cite{MTDNN19}, and many other areas have been achieved by learning from multiple tasks together.
In spite of these promising empirical results, multi-task learning is not well-understood because of the prevalence of \textit{negative transfer} -- when the trained multi-task model performs worse than single-task learning for the target task.
\todo{transition}
In this work, we present a theoretical study to better understand when multi-task learning works better than single-task learning. % for learning from multiple linear regression tasks.
%We consider a setting where the target task has limited labeled data and show
%On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
	\caption{Phase transition as a parameter of model distance.}
	\label{fig_motivation}
\end{figure}
